On Sample Size Needed for Block Bootstrap Confidence Intervals to Have Desired Coverage Rates

### 2023-09-02 Manuscript/manuscript.tex
minor edits; use hyperref

\usepackage{physics} % for \dd

@@

The series were generated by marginally transforming the
AR(1) series  $X_t$ in the simulation study by
\begin{equation*}
W_t = F^{-1}[\Phi(X_t)],
\end{equation*}
where $F^{-1}(p)$ is the quantile function for the unit exponential 
distribution. The true mean and standard deviation parameters are~1. The lag-1
autocorrelation coefficient is not invariant to the
transformation, \citep{hofert2018elements} but its value can be obtained by
\begin{equation*}
\int_{-\infty}^\infty \int_{-\infty}^\infty F^{-1}[\Phi(x)] F^{-1}[\Phi(y)] g_2(x, y; \phi) \dd x \dd y - 1,
\end{equation*}
where $g_2(x, y; \phi)$ is the density of a standard bivariate normal
distribution with correlation~$\phi$. We kept the configuration of
$\phi \in \{-0.4, -0.2, 0.0, 0.2, 0.4\}$, and the corresponding lag-1
autocorrelation coefficients are $\{-0.298, -0.156, 0, 0.170, 0.355\}$.

@@

\begin{figure}[tbp]
  \centering
  \includegraphics[width=\textwidth]{figures/exp_phi_intervals}
  \caption{50 replicate percentile, BC, and recentered percentile CIs for the
    mean, standard deviation, and lag-1 autocorrelation coefficient
    of a stationary series with marginal exponential distribution
    obtained by transforming an AR(1) process with $\phi = 0.4$ with
    sample size $n \in \{800, 1600\}$. For 
    each replicate, the lower and upper bounds of the CIs are displayed, as well 
    as $\hat\theta_n$ (blue circle) and $\bar\theta_n^{B}$ (red cross).}
  \label{fig:eri}
\end{figure}

\jy{change the captions of the other three figures accordingly}
\mc{addressed}

The empirical coverage rates for $\mu$, $\sigma_w$, and $\phi$, as well as 95\%
confidence intervals of the real coverage are displayed in 
\textbf{Figures~\ref{fig:exp_mu}--\ref{fig:exp_phi}}. 
Additionally, another set of 50 CIs was generated for each of the percentile, 
BC, and recentered percentile approaches for exponentially distributed
samples of $n \in \{800, 1600\}$ in Figure~\ref{fig:eri}.

>>>>

\usepackage{physics} % for \dd
\usepackage{hyperref}

@@

The series were generated by marginally transforming the
AR(1) series  $X_t$ in the simulation study by
\begin{equation*}
W_t = F^{-1}[\Phi(X_t)],
\end{equation*}
where $F^{-1}(p)$ is the quantile function for the unit exponential 
distribution. The true mean and standard deviation parameters are~1. The lag-1
autocorrelation coefficient is not invariant to the
transformation, \citep{hofert2018elements} but its value can be obtained by
\begin{equation*}
\int_{-\infty}^\infty \int_{-\infty}^\infty F^{-1}[\Phi(x)] F^{-1}[\Phi(y)] g_2(x, y; \phi) \dd x \dd y - 1,
\end{equation*}
where $g_2(x, y; \phi)$ is the density of a standard bivariate normal
distribution with correlation parameter~$\phi$. We kept the configuration of
$\phi \in \{-0.4, -0.2, 0.0, 0.2, 0.4\}$, and the corresponding lag-1
autocorrelation coefficients are $\{-0.298, -0.156, 0, 0.170, 0.355\}$.

@@

\begin{figure}[tbp]
  \centering
  \includegraphics[width=\textwidth]{figures/exp_phi_intervals}
  \caption{50 replicate percentile, BC, and recentered percentile CIs for the
    lag-1 autocorrelation coefficient 0.355 ($\phi = 0.4$)
    of a stationary series with marginal exponential distribution
    obtained by transforming an AR(1) process with $\phi = 0.4$ with
    sample size $n \in \{800, 1600\}$. For 
    each replicate, the lower and upper bounds of the CIs are displayed, as well 
    as $\hat\theta_n$ (blue circle) and $\bar\theta_n^{B}$ (red cross).}
  \label{fig:eri}
\end{figure}

The empirical coverage rates for $\mu$, $\sigma_w$, and $\phi$, as well as 95\%
confidence intervals of the real coverage are displayed in 
\textbf{Figures~\ref{fig:exp_mu}--\ref{fig:exp_phi}}. 
Additionally, a set of 50 CIs are displayed for each of the percentile, 
BC, and recentered percentile approaches for exponentially distributed
samples of $n \in \{800, 1600\}$ with lag-1 autocorrelation coefficient 0.355
($\phi = 0.4$) in Figure~\ref{fig:eri}.
